---
title: "Git_Question"
author: "Derek Corcoran"
date: "11/29/2019"
output: md_document
always_allow_html: true
---


All the files for this question are in the [following git](https://github.com/derek-corcoran-barrios/El_Soldado):

I am trying to plot a categorical map in leaflet with a categorical legend showing a character vector as labels:


## Load the packages

first I load the required packages


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, cache = T, message = F, warning = F)
```


```{r}
library(rgdal)
library(raster)
library(kableExtra)
library(rasterVis)
library(leaflet)
```

## Then I load the required datasets

```{r mapa}
Codes <- readRDS("Codes.rds")
LandCover <- readRDS("LandCover.rds")
```

if we look at the landcover raster it is a categorical raster that I made with `ratify` from the raster package

```{r}
LandCover
```

I want to have the name attribute as the legend

which works using the `levelplot` function from the rasterVis package:

```{r}
rasterVis::levelplot(LandCover)
```

The data is also repited in the Codes data.frame if it works

```{r Tabla}
kable(Codes, caption = "Tabla de atributos del mapa") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


## Two tests that didn't work

### Test 1

```{r}
pal <- colorFactor(rainbow(10), values(LandCover),
                    na.color = "transparent")

leaflet() %>% addTiles()  %>%  addRasterImage(LandCover, colors = pal, opacity = 0.8) %>%  addLegend(pal = pal, values = values(LandCover),title = "Land Cover", labels = Codes$Selected)
```

### Test 2 

In this second one I thought that adding the labels attribute to the `addLegend` function would do the trick, but it does not work

```{r}
pal <- colorFactor(rainbow(10), values(LandCover),
                    na.color = "transparent")

leaflet() %>% addTiles()  %>%  addRasterImage(LandCover, colors = pal, opacity = 0.8) %>%  addLegend(pal = pal, values = values(LandCover),title = "Land Cover", labels = Codes$Selected)
```
